Binary companions of red clump stars I: \\ catalog and surviving companions

### 2017-08-10 paper/1-catalog/twoface-catalog.tex
titles
author shit
new outline

% to-do list
% ----------
% - write a first draft of the introduction
% - list our assumptions for detection & characterization (TheJoker)
% - list our assumptions for hierarchical inference

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!
% - Where there are defined math symbols (like \pars), use them!

% other notes
% - Binary engulfment reference: https://arxiv.org/pdf/1002.2216.pdf
% -

@@

@@

\title{Binary companions of red clump stars}

\author{Adrian~M.~Price-Whelan}
\affiliation{Department of Astrophysical Sciences,
             Princeton University, Princeton, NJ 08544, USA}
\email{adrn@astro.princeton.edu}
\correspondingauthor{Adrian M. Price-Whelan}

@@

\begin{abstract}\noindent % trust me
% Context
Radial-velocity measurements can be used to find stellar, sub-stellar,
and planetary companions of stars.
In the \apogee\ survey, we have multi-epoch radial-velocity measurements
for many red-giant stars, including many red-clump (\RC) stars.
Spectral analysis of \RC\ stars can be used to deliver masses (with
XXX precision) and 20-ish chemical abundance measurements (with YYY
precision).
% Aims
Here we perform a search for secondary companions of [number] \RC\ stars.
Because the primary-star masses are known, the mass-function degeneracy
is broken and the secondary-companion $m\,\sin i$ values can be inferred.
Also, if the primary and companion are assumed to be co-eval, the
abundances of the \RC\ star can be assumed to represent accurately the
abundances of the secondary.
% Methods
We use a data-driven model (\thecannon) of stellar spectra to deliver
each \RC\ mass and chemical abundances, and a custom-built Monte Carlo
sampler (\thejoker) to deliver (often highly multi-modal) posterior
beliefs about companion $m\,\sin i$, period, and other orbital parameters.
Our sampler permits us to accurately sample even the badly behaved
posterior pdfs obtained when there are as few an NNN observation
epochs per star.
We put these posterior samples---made under an interim prior---into a
hierarchical inference to obtain individual-companion-marginalized
posterior beliefs about the properties of the full secondary-companion
distribution in mass and period.
In this analysis, even stars with only a few observations (and therefore
badly multimodal posterior pdfs) contribute valuable information to the
population inference.
% Results
We deliver a catalog of QQQ companions [that meet some criteria], and
posterior samplings for all [number] stars in the parent sample.
We find that the period and mass distributions [have some properties].
We look for trends with chemical abundances, and we find tentative evidence
for ZZZ and WWW.
\end{abstract}

>>>>

% to-do list
% ----------
% - write a first draft of the introduction
% - list our assumptions for detection & characterization (TheJoker)

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some
%   bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your
%   arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article
%   or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the
%   same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!
% - Where there are defined math symbols (like \pars), use them!

% other notes
% - Binary engulfment reference: https://arxiv.org/pdf/1002.2216.pdf

% Outline:
% - Intro
% - Data (APOGEE description)
% - Methods
%     - Re-measure velocities
%     - The Joker / orbit sampling
% - Results
%     - Catalog of companions (including samplings)
%     - Differences between RGB / RC
%     - Other interesting shit
% - Discussion

@@

\newcommand{\nRC}{XX}
\newcommand{\nRGB}{XX}
\newcommand{\ntotal}{XX}
\newcommand{\ncompanions}{XX}

@@

\title{Binary companions of red clump stars I: \\
       catalog and surviving companions}

\author[0000-0003-0872-7098]{Adrian~M.~Price-Whelan}
\affiliation{Department of Astrophysical Sciences,
             Princeton University, Princeton, NJ 08544, USA}
\email{adrn@astro.princeton.edu}
\correspondingauthor{Adrian M. Price-Whelan}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to find stellar,
sub-stellar, and planetary companions of stars.
The \apogee\ survey has measured multi-epoch but sparse radial velocities for
$> XX$ (mainly red giant) stars.
Though even few observations are useful for detecting companions, such data are
difficult to use for constraining the physical properties of companions because
permitted orbital solutions are highly degenerate.
% Aims
Here we perform a search for secondary companions of \nRC\ red clump (\RC) and
\nRGB\ red giant branch (\RGB) stars that have similar radii to \RC\ stars
observed as part of the \apogee\ survey.
Because the primary-star masses are known, the mass-function degeneracy is
broken and the secondary-companion masses ($m\,\sin i$) can be inferred.
% Methods
We use a custom-built Monte Carlo sampler (\thejoker) combined with prior
measurements of primary masses and stellar parameters to deliver (often highly
multi-modal) posterior beliefs about companion mass, pericenter distance, and
other orbital parameters for the \RC\ and \RGB\ stars.
% Results
We deliver a catalog of \ncompanions\ companions \todo{that meet some criteria},
and posterior samplings for all \ntotal\ stars in the parent sample.
We find \todo{describe} differences between the companions around \RC\ and \RGB\
stars that are \todo{in/consistent} with the theoretical prediction that
stellar companions should not survive the common-envelope \RGB\ phase.
We additionally find trends with chemical abundances, and we find tentative
evidence for ZZZ and WWW.
\end{abstract}
